A comparative analysis of penalized linear mixed models in structured genetic data

### 2020-12-17 main.tex
3.3 how to describe sigma_g^2 / sigma_s^2?

Conversely, LMM-lasso models $\bZ\bgamma$ as a random effect, which corresponds to the LMM model
\begin{equation}
    \label{eqn:lmm_reg}
    \by = \bX_0\bbeta_0 + \bX\bbeta + \bX\bgamma+ \beps,
\end{equation}
$$ \beps \sim N(\boldsymbol{0}, \sigmaee \bI) $$
$$ \bgamma \sim N(\boldsymbol{0}, p^{-1} \sigmagg \bI) \Rightarrow \bX \bgamma \sim N(\boldsymbol{0}, \sigmagg \bK), $$
where $\sigmagg$ is the additive genetic variance, and we assume $\beps \independent \bgamma$. Rather than assuming anything about $\bgamma$ directly, a common representation paramaterizes the model in terms of $\bu=\bX\bgamma$, which yields an equivalent model.

>>>>

Conversely, LMM-lasso models $\bZ\bgamma$ as a random effect, which corresponds to the LMM model
\begin{equation}
    \label{eqn:lmm_reg}
    \by = \bX_0\bbeta_0 + \bX\bbeta + \bX\bgamma+ \beps,
\end{equation}
$$ \beps \sim N(\boldsymbol{0}, \sigmaee \bI) $$
$$ \bgamma \sim N(\boldsymbol{0}, p^{-1} \sigmagg \bI) \Rightarrow \bX \bgamma \sim N(\boldsymbol{0}, \sigmagg \bK), $$
where $\sigmagg$ is the \anna{additive genetic variance}, and we assume $\beps \independent \bgamma$. Rather than assuming anything about $\bgamma$ directly, a common representation paramaterizes the model in terms of $\bu=\bX\bgamma$, which yields an equivalent model.
